### 2016-03-15 thesis/conclusions.tex
poco

In Chapter \ref{ch:recov-mn} \citep{savorgnan2013}, we compared the results obtained by four independent studies 
\citep{grahamdriver2007,sani2011,vika2012,beifiori2012}
that attempted photometric decompositions of similar samples of galaxies with a direct measurement 
of the black hole mass. 
In many cases we found a large discrepancy between the spheroid S\'ersic index measurements 
obtained by different studies for the same galaxy, 
either due to a significantly different choice of model components 
or to other various systematic effects. 
By rejecting the most discrepant S\'ersic index measurements and averaging the remaining ones, 
we were able to recover a strong $M_{\rm BH} - n_{\rm sph}$ correlation, 
which was not found using the individual datasets of three of the four aforementioned studies. 
From this we concluded that some of the galaxy decompositions were not accurate. 
Chapter \ref{ch:recov-mn} emphasises the importance of a correct, physically motivated selection of model components 
and cautions against the several systematics that can affect galaxy decomposition. \\

@@

sequence than previously reported by \citet{grahamscott2013}. 
We did not observe any offset of spheroids with S\'ersic index $n_{\rm sph} < 2$ 

@@

that is, a \emph{red sequence} of early-type galaxies (elliptical+lenticular) 

@@

and a dramatically steeper \emph{blue sequence} of late-type galaxies (spiral) 

@@

appear to be the low-mass continuation of the $M_{\rm BH} - M_{\rm *,sph}$ sequence traced by our spiral galaxies. 

@@

In Chapter \ref{ch:mn} \citep{paperIII}, 
we analysed the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
and found that in the former early- and late-type galaxies split into two separate correlations, 
whereas in the latter all galaxies -- irrespective of their morphological type -- define a single correlation. 
Our $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
show consistent amount of intrinsic scatter, 
in agreement with the results from \citet{grahamdriver2007}. 
The present dataset allows one to explore also the relation of the black hole mass with 
the spheroid central surface density, $\mu_{\rm 0, sph}$, 
and the spheroid deprojected central stellar density, $\rho_{\rm *,0,sph}$. \\

In Chapter \ref{ch:msigma}, we focused on the $M_{\rm BH} - \sigma$ diagram 
and in particular on the over-massive black holes that have been reported to exist 
at the high-mass end of the correlation. 
\citet{volontericiotti2013} explained the presence of the outlying black holes 
as a natural consequence of the fact that their host Central Cluster Galaxies (CCGs) have experienced more dry mergers 
than any other galaxy, 
since dry mergers are expected to increase the black hole mass 
and ``conserve'' the stellar velocity dispersion. 
We tested and disproved this scenario for 23 core-S\'ersic galaxies, 
using the ratio between black hole mass and stellar mass deficit as a proxy 
for the number of dry mergers experienced by a galaxy \citep{merritt2006}. 
This was confirmed by a second test using the central kinematic classification of 37 galaxies. 
Our analysis suggests that 
the merger history of the CCGs hosting over-massive black holes in the $M_{\rm BH} - \sigma$ diagram 
is not exceptional, 
therefore these galaxies should be considered as legitimate members of the $M_{\rm BH} - \sigma$ correlation. 
An alternative possibility for the CCGs is that their partially depleted core 
has been replenished by stars, globular clusters and nuclear star clusters 
acquired from minor dry mergers, 
where the accreted satellite galaxies do not host a massive black hole. 
However, high-resolution cosmological simulations seem to favour an ``inside-out'' formation scenario 
for early-type galaxies, 
where minor mergers only contribute to the build-up of the external envelope of high-mass galaxies 
(e.g.~\citealt{wellons2016}). 
It should also be noted that evidence is accumulating against the ``naive'' assumption 
that low-mass galaxies do not host any central massive black hole 
(e.g.~\citealt{Baldassare2015,Graham2016LEDA}). \\

@@

If also their black holes has had little or no mass accretion since $z = 2$, 

@@

Therefore, finding a larger number of local galaxies with the same charachteristics of the aforementioned five 

@@

rather than on the \emph{spheroid} properties, 
therefore a number of these candidates might not be real descendant of the $z=2$ population\footnote{Some 

@@

The same holds for the simulated compact massive galaxies of \citet{wellons2016}. 
It would be interesting to perform photometric decompositions for these 76 candidates 
and select only those with compact massive \emph{spheroids}.

>>>>

In Chapter \ref{ch:recov-mn} \citep{savorgnan2013}, we compared the results obtained by four independent studies 
\citep{grahamdriver2007,sani2011,vika2012,beifiori2012}
that attempted photometric decompositions of similar samples of galaxies with a direct measurement 
of the black hole mass. 
In many cases we found a large discrepancy between the spheroid S\'ersic index measurements 
obtained by different studies for the same galaxy, 
either due to a significantly different choice of model components 
or to other various systematic effects. 
By rejecting the most discrepant S\'ersic index measurements and averaging the remaining ones, 
we were able to recover a strong $M_{\rm BH} - n_{\rm sph}$ correlation, 
which was not found using the individual datasets of three of the four aforementioned studies. 
From this we concluded that some of their galaxy decompositions were not accurate. 
Chapter \ref{ch:recov-mn} emphasises the importance of a correct, physically motivated selection of model components 
and cautions against the several systematics that can affect galaxy decomposition. \\

@@

sequence than previously reported \citep{grahamscott2013}. 
Looking at the spheroids with S\'ersic index $n_{\rm sph} < 2$, 
we did not observe any systematic offset 

@@

that is, a \emph{red sequence} of early-type (elliptical+lenticular) galaxies 

@@

and a dramatically steeper \emph{blue sequence} of late-type (spiral) galaxies 

@@

appears to be the low-mass continuation of the $M_{\rm BH} - M_{\rm *,sph}$ sequence traced by our spiral galaxies. 

@@

In Chapter \ref{ch:mn} \citep{paperIII}, 
we analysed the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
and found that in the former early- and late-type galaxies split into two separate correlations, 
whereas in the latter all galaxies -- irrespective of their morphological type -- define a single correlation. 
Our $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
show consistent amount of intrinsic scatter, 
in agreement with the results from \citet{grahamdriver2007}. 
The present dataset allows one to explore also the correlation of black hole mass with 
spheroid central surface density, $\mu_{\rm 0, sph}$, 
and spheroid deprojected central stellar density, $\rho_{\rm *,0,sph}$. \\

In Chapter \ref{ch:msigma}, we focused on the $M_{\rm BH} - \sigma$ diagram 
and in particular on the over-massive black holes that have been reported to exist 
at the high-mass end of the correlation. 
\citet{volontericiotti2013} explained the presence of the outlying black holes 
as a natural consequence of the fact that their host Central Cluster Galaxies (CCGs) have experienced more dry mergers 
than any other galaxy, 
since dry mergers are expected to increase the black hole mass 
and ``conserve'' the stellar velocity dispersion. 
We tested and disproved this scenario for 23 core-S\'ersic galaxies, 
using the ratio between black hole mass and stellar mass deficit as a proxy 
for the number of dry mergers experienced by a galaxy \citep{merritt2006}. 
This was confirmed by a second test using the central kinematic classification of 37 galaxies. 
Our analysis suggests that 
the merger history of the CCGs hosting over-massive black holes in the $M_{\rm BH} - \sigma$ diagram 
is not exceptional, 
therefore these galaxies should be considered as legitimate members of the $M_{\rm BH} - \sigma$ correlation. 
An alternative possibility for the CCGs is that their partially depleted cores 
have been replenished by stars, globular clusters and nuclear star clusters 
acquired from minor dry mergers, 
where the accreted satellite galaxies did not host a massive black hole. 
However, high-resolution cosmological simulations seem to favour an ``inside-out'' formation scenario 
for early-type galaxies, 
where minor mergers only contribute to the build-up of the external envelope of high-mass galaxies 
(e.g.~\citealt{wellons2016}). 
It should also be noted that evidence is accumulating against the ``naive'' assumption 
that low-mass galaxies do not host any central massive black hole 
(e.g.~\citealt{Baldassare2015,Graham2016LEDA}). \\

@@

If also their black holes have had little or no mass accretion since $z = 2$, 

@@

Therefore, finding a larger number of local galaxies with the same charachteristics as the aforementioned five 

@@

rather than the \emph{spheroid} properties, 
therefore a number of these candidates might not be real descendants of the $z=2$ population\footnote{Some 

@@

The same concern holds for the simulated compact massive galaxies of \citet{wellons2016}. 
It would be interesting to perform photometric decompositions 
for the observed 76 compact massive galaxies of \citet{saulder2015} 
and for those simulated by \citet{wellons2016}, 
to select only those with compact massive \emph{spheroids}.

\citet{kormendy2011} and \citet{kormendyho2013} argued that black holes correlate only 
with the remnants of major mergers, i.e.~classical bulges and elliptical galaxies, 
and that
